\documentclass[10pt, fleqn, a4paper]{report}
%a4paper : 21.0cm * 29.7cm

\usepackage{xeCJK}
\setCJKmainfont[BoldFont=STFangsong, ItalicFont=STKaiti]{STSong}
\setCJKsansfont[BoldFont=STHeiti]{STSong}
\setCJKmonofont{STFangsong}

\usepackage{amsmath}
\usepackage{amssymb,amsfonts}
\usepackage{tabularx}
%\usepackage{longtable}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{tikz}
\usepackage[T1]{fontenc}
\usepackage{upquote}
\usepackage[colorlinks, linkcolor=blue, anchorcolor=blue, citecolor=blue, urlcolor=blue]{hyperref}
\usepackage{ltxtable, filecontents}
\usepackage{mathrsfs}  

\setlength{\topmargin}{0cm}

\setlength{\oddsidemargin}{0.4cm}
\setlength{\evensidemargin}{0.4cm}
\setlength{\hoffset}{-0.2in}
\setlength{\textwidth}{440pt}
\setlength{\textheight}{650pt}
\setlength{\parindent}{0pt}
\setlength{\parskip}{5pt}

\setlength{\mathindent}{0pt}

\usepackage{color}
\usepackage{xcolor}
\usepackage{listings}

\usepackage{caption}
\DeclareCaptionFont{white}{\color{white}}
\DeclareCaptionFormat{listing}{\colorbox{lightgray}{\parbox{\textwidth}{#1#2#3}}}
\captionsetup[lstlisting]{format=listing,labelfont=white,textfont=white}

\definecolor{mygreen}{rgb}{0,0.6,0}
\definecolor{mygray}{rgb}{0.5,0.5,0.5}
\definecolor{mymauve}{rgb}{0.58,0,0.82}

\lstset{
	basicstyle=\footnotesize,
	breaklines=true,
	commentstyle=\color{mygreen},
	numbers=left,
	numbersep=5pt,
	numberstyle=\tiny\color{mygray},
	stringstyle=\color{mymauve},
	showstringspaces=false,
	showspaces=false,
	showtabs=false,
	tabsize=2,
	framexleftmargin=10mm,
	frame=none,
	backgroundcolor=\color[RGB]{245,245,244},
	keywordstyle=\bf\color{blue},
	identifierstyle=\bf,
	numberstyle=\color[RGB]{0,192,192},
	commentstyle=\it\color[RGB]{0,96,96},
	stringstyle=\rmfamily\slshape\color[RGB]{128,0,0}
}

\newcommand{\tabincell}[2]{\begin{tabular}{@{}#1@{}}#2\end{tabular}}

\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}


\begin{document}

\begin{titlepage}
\vspace*{40mm}
\begin{center}
{\Huge Homework \quad 7}\\[30mm]

{\Large 5130309059 \quad \quad 李佳骏}\\[3mm]
\texttt{taringlee@sjtu.edu.cn}\\[10mm]

2015.11.29

\end{center}
\end{titlepage}

\section*{Exercise 7.3}
Let the function $f_m(x_1,...,x_m)$ be $1$ iff the $m$-bit string $x_1,...,x_m$ contains two consecutive 1s. Prove that $D^{worst}(f_m) = \Theta(m)$.

It's easy to show that for $f_m(x_1,...,x_m)$, $D^{worst}(f) \leq \frac{m}{2} + 1$. Because for any partition $S$ : $T$, the player with the least number of bits can send them to the other player). Hence we will find a single hard partition to prove lower bounds for the worst-cast communication complexity.

In this case, the hard petition is the odd bits versus the even bits. Computing $f_m$, according to this partition, is equivalent to computing the function $f_l(x,y)$ ($f_l(x,y)$ will return 1 iff $\exists y_i = 1$ s.t. $x_i = y_i = 1$ or $x_{i+1} = y_i = 1$). In the regular two-party model, we can easily show that the disjointness function, DISJ, on ${0,1}^{\frac{m}{2}} \times {0,1}^{\frac{m}{2}}$ can be reduced to the subquestion corresponding to $S$ and $T$.that at least $d = \Omega(\frac{m}{2})$ bits are required to solve the subquestion. the worst case shows that $D^{worst}(f_M) \geq D(f_l) \geq \Omega(\frac{m}{2})$. Conclude $D^{worst}(f_m) = \Theta(m)$.

\section*{Exercise 7.15$^{*}$}
The undirected $s-t$-connectivity problem, USTCON, accepts as input a graph on $l$ vertices (that is, $m = \binom{l}{2}$ input bits representing the edges), and outputs 1 if and only if there exists a path between vertices $s$ and $t$ in the input graph($s \neq t$). Prove that for all $n$, $D^{n-best}(\mathrm{USTCON}) = \Omega(\frac{n}{l})$. Conclude that $D^{best}(\mathrm{USTCON}) = \Omega(\sqrt{m})$.

Define $G_A(V_A,E_A)$ consist of inputs to Alice and as same relationship with $G_B(V_B,E_B)$ and Bob. Consider there are n edges in each graph. Let $d = \frac{n}{4l}$. Construct the ordered edge set of Alice$$S_A := \{(u_i, v_i) \in E_A \mid v_i \neq v_j(i \neq j), v_i \neq u_j\}, |S_A| = d$$
%Notice that it's allowable that $u_i = u_j$. 

Here is the proof of the Existence of $S_A$. If $\exists p \in G_A$, such that $deg_{G_A}(p) \geq d$ (function $deg_{G}(x)$ means the degree of $x$ in graph $G$). we can choose each $u_i = p$. Otherwise, we notice that for each vertex $deg_{G_A}(x) \leq d - 1$. If we choose one edge $(u,v)$ into $S_A$, we can not choose other edges which endpoint is $u$ or $v$. Thus the choice would fix at most $2d-3$ edges and there are at most$d(2d-3)$ edges we fixed. Because $n \leq m < \frac{l^2}{2}$, $d(2d-3) < n(\frac{n}{8l^2}-\frac{3}{4l}) < n$, it's enough to choose $d$ times.

Thus consider the graph $G_B$. Define $G'_B(V'_B, E'_B)$, such that $V'_B := \{x \in V_B \mid x \neq u_i,v_i : \forall (u_i,v_i) \in S_A\}$, $E'_B := \{ (u,v) \in E_B \mid u,v \in V'_B \}$. Because $|E'_B| \geq n - 2d \cdot l \geq \frac{n}{2}$, it's enough to construct the similar ordered edge set of Bob$$S_B := \{(u'_i, v'_i) \in E'_B \mid v'_i \neq v'_j(i \neq j), v'_i \neq u'_j\}, |S_B| = d$$

Now there are four ordered point sets($V_u,V_v,V_{u'},V_{v'}$), two fixed vertex $s$ and $t$ and two ordered edge sets$S_A, S_B$. And we formulate other edges to show that the disjointness function DISJ on ${0,1}^d \times {0,1}^d$ can be reduced to this problem corresponding to $S_A$ and $S_B$. For all $u_i \neq u_j(u_i,u_j \in V_u)$, add edge $(u_i, u_j)$. For all $u'_i \neq u'_j(u'_i,u'_j \in V_{u'})$, add edge $(u'_i, u'_j)$. For all $i \in [d]$, ensure edges $(s, u_i), (v_i,v'_i), (u_i, t)$ are all added(If not, we added them). Now there are $d$ feasible paths from $s$ to $t$, path $i$ is feasible iff $(u_i,v_i)$, $(u'_i,v'_i)$ would be true(both corresponding input bits to 1). Hence that at least $d = \Omega(\frac{n}{l})$ bits are required to solve USTCON by reducing to DISJ. Finally, when $n = \frac{m}{2}$, $D^{best}(f) = D^{\frac{m}{2}-best}(f) = \Omega(l) = \Omega(\sqrt{m})$.

\end{document}